\cvsection{Experience}
\begin{cventries}
  \cventry
    {equensWorldline}
    {Project Security Officer}
    {Lyon, France}
    {Jun. 2017 - Present}
    {
      \begin{cvitems}
        \item {Acted as Security Officer for the company's HCE solution, which includes backend services, Android applications and a mobile SDK.}
        \item {Ensured on-going compliance of a high-risk project with standards such as PCI-DSS, PCI-CP, GDPR.}
        \item {Maintained all accreditations, and ensured all new relevant releases were scheduled for audit.}
        \item {Managed internal/external audits, follow-ups and action plans with audit groups, issuers and schemes of international origins.}
      \end{cvitems}
    }
  \cventry
    {equensWorldline}
    {CAT Manager \& Backend Developer (Devops)}
    {Lyon, France}
    {May. 2015 - Jun. 2017}
    {
      \begin{cvitems}
        \item {Managed the HCE Customer Acceptance Testing backend platform for customers in Belgium, Germany, Czech Republic and France.}
        \item {Developed the HCE backend consisting of an administration interface and two Java/Spring services exposing REST APIs.}
        \item {Designed and developed a "Docker as a Service" platform running on multiple Mesos clusters, used as an internal software forge.}
        \item {Developed several Java/Spring backend services for Orange's mobile applications (french ISP and mobile carrier).}
      \end{cvitems}
    }
  \cventry
    {Worldline}
    {Operations Manager}
    {Lyon, France}
    {Oct. 2012 - Jun. 2016}
    {
      \begin{cvitems}
        \item {Oversaw and managed regulatory compliance with the QoS throughout the backend platform for Orange mobile applications.}
        \item {Conducted weekly incidents and changes followup with the customers, as well as a monthly capacity planning.}
        \item {Trained new recruits to operate a web application, manage incident/changes and better coding for a distributed highly-scaled service.}
        \item {Managed two near-shore technicians helping with technical analysis and completing recurring tasks on the backend platform.}
      \end{cvitems} 
    }
  \cventry
    {Worldline}
    {Software Engineer Trainee}
    {Lyon, France}
    {Jun. 2011 - Dec. 2011}
    {
      \begin{cvitems}
        \item {Developed the front and back ends of SFR's webmail (french ISP and mobile network operator).}
        \item {Improved the webmail performances by monitoring system metrics and tuning the JVM memory allocation and garbage collection.}
      \end{cvitems}
    }
    \cventry
    {Netissime}
    {Software Engineer Trainee}
    {Lyon, France}
    {Jun. 2010 - Aug. 2010}
    {
      \begin{cvitems}
        \item {Installed and configured a new shared hosting infrastructure in a datacenter.}
        \item {Developed the new provisioning system for user accounts.}
      \end{cvitems}
    }
    \cventry
    {Bayard Service Web}
    {Software Engineer Trainee}
    {Chambéry, France}
    {Jun. 2009 - Aug. 2009}
    {
      \begin{cvitems}
        \item {Developed a new software for managing subscriptions to the magazines of the French editor Bayard Presse.}
      \end{cvitems}
    }
\end{cventries}
